---
# Research Competencies Self-Assessment — surveydown app.
# Modules A (internal) + B (proposed work) + C (research design), fully wired.

theme-settings:
  theme: default
  barposition: top
  footer-left: "Grantee Research Competencies Self-Assessment"
  footer-right: "Research Competencies Self-Assessment"

survey-settings:
  mode: database         # database = persist responses to PostgreSQL (creds via SD_* env vars).
                         # For local testing WITHOUT a database, flip this to `preview`.
  show-previous: true
  use-cookies: false
  auto-scroll: false
  rate-survey: false
  system-language: en
  highlight-unanswered: true
  highlight-color: blue
  capture-metadata: true
  all-required: false
  required:
    - B1
    - B2
    - B3
---

```{r}
library(surveydown)
```

<!-- ====================================================================== -->
<!-- MODULE A — Internal (program officer). In production this is a separate  -->
<!-- officer-facing form; here it seeds routing + drives Module B defaults.   -->
<!-- ====================================================================== -->

--- a_internal

# Module A — Internal (Program Officer)

*For context prior to administering the survey to a grantee team, the responsible program officer fills out the following based on the proposal. These answers drive which modules/domains the respondents receive.*

```{r}
sd_question(
  type   = "mc_multiple",
  id     = "A1",
  label  = "A1. Which grantee research method competencies would you like to assess?",
  option = c("Qualitative study" = "1", "Quantitative study" = "2", "Review" = "3")
)

sd_question(
  type   = "mc_multiple",
  id     = "A2",
  label  = "A2. What is the purpose of the research as defined in the proposal?",
  option = c(
    "Feasibility or acceptability study" = "1",
    "Process or performance study"       = "2",
    "Validation of a measurement tool"   = "3",
    "Impact / causal inference study"    = "4",
    "Implementation research"            = "5"
  )
)

sd_question(
  type  = "numeric",
  id    = "A3",
  label = "A3. How many key staff are involved in the work? (1–99)"
)
```

<!-- ====================================================================== -->
<!-- MODULE B — Proposed Work (respondent confirms officer's entries).        -->
<!-- B1/B2/B3 are the master drivers for all downstream skip logic + grids.   -->
<!-- ====================================================================== -->

--- b_proposed

# Module B — Proposed Work

Thank you for taking the time to complete this self-assessment. It will help us
understand your team's research skills and offer resources that may strengthen
them. The following questions were pre-filled by a program officer based on your
proposal — please confirm they are accurate.

**Proficiency levels used throughout:**

- **Entry / Novice:** developing awareness, building knowledge, limited experience.
- **Proficiency / Skilled:** applying knowledge routinely, moderate experience, solves problems as they arise.
- **Mastery / Expert:** using knowledge fluently, extensive experience, sought out for input or mentorship.

```{r}
sd_question(
  type   = "mc_multiple",
  id     = "B1",
  label  = "B1. Which research methods are included in the proposal?",
  option = c("Qualitative study" = "1", "Quantitative study" = "2", "Review" = "3")
)

sd_question(
  type   = "mc_multiple",
  id     = "B2",
  label  = "B2. What is the purpose of the research as defined in the proposal?",
  option = c(
    "Feasibility or acceptability study" = "1",
    "Process or performance study"       = "2",
    "Validation of a measurement tool"   = "3",
    "Impact / causal inference study"    = "4",
    "Implementation research"            = "5"
  )
)

sd_question(
  type  = "numeric",
  id    = "B3",
  label = "B3. How many key staff are involved in the work? Key staff are those responsible for technical leadership of the proposed work. (1–99)"
)
```

<!-- ====================================================================== -->
<!-- MODULE C — Research Design                                               -->
<!-- Grids are rendered from server-side definitions (count_grid.R) so their  -->
<!-- rows can react to B1/B2/B3. Static questions (C2 gate, C8/C14 matrices)  -->
<!-- are declared inline.                                                     -->
<!-- ====================================================================== -->

--- c_formulating_rq

# Module C — Research Design

*This module asks about your team's experience designing studies related to your
proposal: formulating questions, study design, and sampling design.*

## Formulating research questions

```{r}
# C1 count grid — rendered from server (rows b–f gate on B2; [q] piped from B1).
sd_output("C1", type = "question")
```

--- c_study_design

## Study design

```{r}
sd_question(
  type   = "mc_buttons",
  id     = "C2",
  label  = "C2. Do key staff have experience designing [quantitative or qualitative] research studies?",
  option = c("Yes" = "1", "No" = "0")
)

# C3–C7 grids (shown/hidden via sd_show_if in app.R; C2=No skips the page).
sd_output("C3", type = "question")
sd_output("C4", type = "question")
sd_output("C5", type = "question")
sd_output("C6", type = "question")
sd_output("C7", type = "question")
```

--- c_sampling

## Sampling design

```{r}
# C8 — yes/no per row (matrix). Rows gate on B1.
sd_output("C8", type = "question")

# C9 quantitative sampling considerations (shown if C8a or C8b = Yes).
sd_output("C9", type = "question")
```

--- c_sampling_prob

### Sampling methods

```{r}
sd_output("C10", type = "question")   # probability sampling (always shown)
sd_output("C11", type = "question")   # non-probability sampling (always shown)
sd_output("C12", type = "question")   # other quant considerations (if C8b = Yes)
sd_output("C13", type = "question")   # qualitative sampling (if C8c = Yes)
```

--- c_ethics

## Ethics

```{r}
# C14 — IRB approval yes/no per row (rows gate on B1).
sd_output("C14", type = "question")

sd_question(
  type  = "textarea",
  id    = "C15",
  label = "C15. Please note any ethics, confidentiality, or child-protection certificates of key staff. (File upload is enabled in the deployed version.)"
)
```

--- end

## End of Modules A–C

Thank you. In the full survey, Modules D–H (Data Collection Tools, Fieldwork,
Data Analysis, Interpretation, Communicating Findings) follow here.

Your responses are saved locally in preview mode.

```{r}
sd_close()
```
