---
# Research Competencies Self-Assessment — surveydown app.
# Modules A (internal) + B + C + D; leader-nominate routing (Task A).

theme-settings:
  theme: default
  barposition: top
  footer-left: "Grantee Research Competencies Self-Assessment"
  footer-right: "Research Competencies Self-Assessment"

survey-settings:
  mode: database         # database = persist to PostgreSQL (creds via SD_* env vars).
                         # For local testing WITHOUT a database, flip this to `preview`.
  show-previous: true
  use-cookies: false
  auto-scroll: false
  rate-survey: false
  system-language: en
  highlight-unanswered: true
  highlight-color: blue
  capture-metadata: true
  all-required: false
  required:
    - B1
    - B2
    - B3
---

```{r}
library(surveydown)
```

<!-- ====================================================================== -->
<!-- MODULE A — Internal (program officer). In production this is a separate  -->
<!-- officer-facing form; here it seeds routing + drives Module B defaults.   -->
<!-- Kept as the START page so every respondent has a stable first page; the   -->
<!-- leader-only nominate page follows and is skipped for non-leaders (app.R). -->
<!-- ====================================================================== -->

--- a_internal

# Module A — Internal (Program Officer)

*For context prior to administering the survey to a grantee team, the responsible program officer fills out the following based on the proposal. These answers drive which modules/domains the respondents receive.*

```{r}
sd_question(
  type   = "mc_multiple",
  id     = "A1",
  label  = "A1. Which grantee research method competencies would you like to assess?",
  option = c("Qualitative study" = "1", "Quantitative study" = "2", "Review" = "3")
)

sd_question(
  type   = "mc_multiple",
  id     = "A2",
  label  = "A2. What is the purpose of the research as defined in the proposal?",
  option = c(
    "Feasibility or acceptability study" = "1",
    "Process or performance study"       = "2",
    "Validation of a measurement tool"   = "3",
    "Impact / causal inference study"    = "4",
    "Implementation research"            = "5"
  )
)

sd_question(
  type  = "numeric",
  id    = "A3",
  label = "A3. How many key staff are involved in the work? (1–99)"
)
```

<!-- ====================================================================== -->
<!-- NOMINATE — leader-only page (comes AFTER a_internal so the skip fires on  -->
<!-- page advance). Non-leaders are skipped past it via sd_skip_if(!is_leader).-->
<!-- Leader enters colleague emails -> tokenized invite links (simulate mode:  -->
<!-- written to outputs/invites/ + shown on screen).                          -->
<!-- ====================================================================== -->

--- rt_nominate_page

# Invite your colleagues

*You have been identified as the team lead. Enter the email addresses of the
colleagues you would like to complete this assessment (comma- or space-separated).
Each will receive their own personal survey link.*

```{r}
sd_question(
  type  = "textarea",
  id    = "rt_nominate_emails",
  label = "Colleague email addresses"
)
```

```{r}
shiny::actionButton("rt_nominate_btn", "Generate invite links")
shiny::uiOutput("rt_nominate_result")
```

<!-- ====================================================================== -->
<!-- MODULE B — Proposed Work (respondent confirms officer's entries).        -->
<!-- B1/B2/B3 are the master drivers for all downstream skip logic + grids.   -->
<!-- ====================================================================== -->

--- b_proposed

# Module B — Proposed Work

Thank you for taking the time to complete this self-assessment. It will help us
understand your team's research skills and offer resources that may strengthen
them. The following questions were pre-filled by a program officer based on your
proposal — please confirm they are accurate.

**Proficiency levels used throughout:**

- **Entry / Novice:** developing awareness, building knowledge, limited experience.
- **Proficiency / Skilled:** applying knowledge routinely, moderate experience, solves problems as they arise.
- **Mastery / Expert:** using knowledge fluently, extensive experience, sought out for input or mentorship.

```{r}
sd_question(
  type   = "mc_multiple",
  id     = "B1",
  label  = "B1. Which research methods are included in the proposal?",
  option = c("Qualitative study" = "1", "Quantitative study" = "2", "Review" = "3")
)

sd_question(
  type   = "mc_multiple",
  id     = "B2",
  label  = "B2. What is the purpose of the research as defined in the proposal?",
  option = c(
    "Feasibility or acceptability study" = "1",
    "Process or performance study"       = "2",
    "Validation of a measurement tool"   = "3",
    "Impact / causal inference study"    = "4",
    "Implementation research"            = "5"
  )
)

sd_question(
  type  = "numeric",
  id    = "B3",
  label = "B3. How many key staff are involved in the work? Key staff are those responsible for technical leadership of the proposed work. (1–99)"
)
```

<!-- ====================================================================== -->
<!-- MODULE C — Research Design                                               -->
<!-- Grids are rendered from server-side definitions (count_grid.R) so their  -->
<!-- rows can react to B1/B2/B3. Static questions (C2 gate, C8/C14 matrices)  -->
<!-- are declared inline.                                                     -->
<!-- ====================================================================== -->

--- c_formulating_rq

# Module C — Research Design

*This module asks about your team's experience designing studies related to your
proposal: formulating questions, study design, and sampling design.*

## Formulating research questions

```{r}
# C1 count grid — rendered from server (rows b–f gate on B2; [q] piped from B1).
sd_output("C1", type = "question")
```

--- c_study_design

## Study design

```{r}
sd_question(
  type   = "mc_buttons",
  id     = "C2",
  label  = "C2. Do key staff have experience designing [quantitative or qualitative] research studies?",
  option = c("Yes" = "1", "No" = "0")
)

# C3–C7 grids (shown/hidden via sd_show_if in app.R; C2=No skips the page).
sd_output("C3", type = "question")
sd_output("C4", type = "question")
sd_output("C5", type = "question")
sd_output("C6", type = "question")
sd_output("C7", type = "question")
```

--- c_sampling

## Sampling design

```{r}
# C8 — yes/no per row (matrix). Rows gate on B1.
sd_output("C8", type = "question")

# C9 quantitative sampling considerations (shown if C8a or C8b = Yes).
sd_output("C9", type = "question")
```

--- c_sampling_prob

### Sampling methods

```{r}
sd_output("C10", type = "question")   # probability sampling (always shown)
sd_output("C11", type = "question")   # non-probability sampling (always shown)
sd_output("C12", type = "question")   # other quant considerations (if C8b = Yes)
sd_output("C13", type = "question")   # qualitative sampling (if C8c = Yes)
```

--- c_ethics

## Ethics

```{r}
# C14 — IRB approval yes/no per row (rows gate on B1).
sd_output("C14", type = "question")

sd_question(
  type  = "textarea",
  id    = "C15",
  label = "C15. Please note any ethics, confidentiality, or child-protection certificates of key staff. (File upload is enabled in the deployed version.)"
)
```

--- d_tools

## Data Collection Tools

```{r}
# Module D. D1 selector (D1a/b/c) gates three sub-sections. Rows gate on B1.
sd_output("D1", type = "question")
```

--- d_secondary

### Tools to collect secondary data

```{r}
# Shown only if D1a = Yes (page-skip in app.R). D2 yn matrix + D3 count grid.
sd_output("D2", type = "question")
sd_output("D3", type = "question")
```

--- d_surveys

### Surveys

```{r}
# Shown only if D1b = Yes. D4 yn matrix + D5 count grid.
sd_output("D4", type = "question")
sd_output("D5", type = "question")
```

--- d_protocols

### Interview and focus group protocols

```{r}
# Shown only if D1c = Yes. D6 yn matrix + D7 count grid.
sd_output("D6", type = "question")
sd_output("D7", type = "question")
```

--- end

## End of Modules A–D

Thank you. In the full survey, Modules E–H (Fieldwork, Data Analysis,
Interpretation, Communicating Findings) follow here.

Your responses are saved locally in preview mode.

```{r}
sd_close()
```
